\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{multicol} % in the preamble

\usepackage[scale=0.75, top=1.4cm, bottom=2.5cm, left=1cm, right=1cm]{geometry} 

\firstname{Hubert} % Your first name
\familyname{Siwkin} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{Warsaw, Poland}{}
\mobile{(+48) 724-501-166}
\email{hsiwkin@gmail.com}

\begin{document}

\makecvtitle % Print the CV title
\vspace{-1.5em}
\section{Experience}

\cventry{May 2025 - Present}{Senior Fullstack Engineer}{\textsc{\newline ClickUp}}{}{}{
\begin{itemize}
    \item Worked on ClickUp's import platform, supporting complex customer data migrations from external productivity and project management tools.
    \item Built and maintained TypeScript/NestJS backend services for import workflows involving tasks, comments, attachments, subtasks, and project mappings.
    \item Contributed to Temporal-based workflows and used Angular, Datadog, Tilt, and Harness across development, debugging, and production rollout processes.
    \item Leveraged AI-assisted development tools such as Cursor and Claude Code to accelerate codebase exploration, implementation, and refactoring.
\end{itemize}
}

\cventry{Aug. 2024 - Feb. 2025}{Principal Engineer}{\textsc{\newline Circa}}{}{}{
Provided leadership with hands-on programming using modern frameworks (React, NestJS, Next.js) and robust databases (PostgreSQL, Redis), leveraging AWS and Railway for cloud infrastructure to deliver scalable solutions:
\begin{itemize}
    \item \textbf{Leadership \& Strategy:}
    \begin{itemize}
        \item Managed and mentored a cross-functional team, planned sprints, and established best practices through code reviews.
        \item Collaborated closely with the lead designer to define application vision, version scopes, and release strategies.
    \end{itemize}
    \item \textbf{Technical Contributions:}
    \begin{itemize}
        \item Designed and developed a large-scale search platform processing millions of records, optimizing SQL queries, and managing database migrations.
        \item Designed and implemented an AI-powered LCA assistant with features including AI-driven text and image analysis, interactive Q\&A, WebSocket-based real-time chat, and chunked file upload support.
        \item Leveraged AWS services (S3, Bedrock) and Railway for cloud infrastructure and deployment.
    \end{itemize}
\end{itemize}
}


\cventry{Jan. 2023 - Aug. 2024}{Technical Lead}{\textsc{\newline Beesafe}}{}{}{
Combined leadership with hands-on technical contributions, leveraging a modern tech stack—Express, NestJS, and React for development; PostgreSQL and Redis for data management; and Azure with Kubernetes for scalable deployment—to architect robust solutions:
\begin{itemize}
    \item \textbf{Technical Architecture \& Cross-Company Integration:}
    \begin{itemize}
        \item Designed scalable and efficient architectures for core company services.
        \item Provided technical support and mentorship to full-stack developers, improving team skills and project outcomes.
        \item Led an AI-based data scraping project.
        \item Designed API contracts with internal teams and external partners to ensure seamless service integration.
        \item Built and maintained payment processing systems, handling both incoming and outgoing transactions, including installment plans and automated financial reporting. 
    \end{itemize}
    \item \textbf{Project Leadership:}
    \begin{itemize}
        \item Defined technical roadmaps, driving code refactoring, new features, and architectural improvements in collaboration with company leadership and other team leads.
        \item Collaborated with the DevOps team to optimize deployments using Kubernetes and Azure, ensuring robust performance of services across both development and production environments.
        \item Collaborated with representatives from various Compensa subsidiaries to standardize solutions and integrate best practices across companies.
    \end{itemize}
\end{itemize}
}


\cventry{Mar. 2020 - Feb. 2023}{Full Stack Developer}{\textsc{\newline Beesafe}}{}{}{
    Developed an insurance application from scratch using a microservice architecture:
	\begin{itemize}
    	\item Managed integration with external services:
    	\begin{itemize}
        	\item Evaluated and compared different vendors by testing and analyzing their APIs and documentation to select optimal solutions.
        	\item Collaborated in designing the integration architecture to ensure effective service communication.
    	\end{itemize}
    	\item Developed and maintained a microservice application:
    	\begin{itemize}
    	    \item Implemented services using Node.js, TypeScript, Express.js, and RabbitMQ; managed databases with PostgreSQL and Redis; authored comprehensive documentation including architectural diagrams; conducted testing with Jest.
    	    \item Deployed microservices to a Kubernetes cluster and worked on CI/CD pipelines using GitHub Actions; performed log analysis with Grafana and Loki.
    	\end{itemize}
    	\item Assisted in the recruitment and onboarding of new team members, ensuring a smooth transition and integration into the development team.
    \end{itemize}
}


\cventry{Dec. 2018 - Feb. 2020}{Software Engineer}{\textsc{\newline Samsung R\&D}}{}{}{
    \begin{itemize}
        \item Built a WYSIWYG VS Code extension that enabled developers to create Samsung mobile and watch apps using JavaScript and Node.js.
        \item Contributed to the Tizen Advanced UI framework by building developer tooling with JavaScript and internal libraries.
    \end{itemize}
}

% \subsection{Vocational}
\cventry{July 2017 - Nov. 2018}{JavaScript Developer}{\textsc{\newline 10Clouds}}{}{}{
    Led frontend development for Angular 2+ apps with interactive D3.js charts and contributed across web apps built with Angular, React, and Redux.
}

% \subsection{Vocational}
\cventry{Jun. 2016 -- May 2017}{Programmer}{\textsc{\newline EY}}{}{}{
    \begin{itemize}
     \item Built web applications for data analysis, document validation, and benchmarking using Angular 2, React, TypeScript, Node.js, and PostgreSQL.
     \item Built a Bitcoin traffic tracker, an Elasticsearch-based search tool, and a news feed app with a dashboard and user authorization.
    \end{itemize}
}


\cventry{May 2016 -- May 2016}{Programmer / Web Developer}{\textsc{\newline Lionbridge Technologies, Inc., Warsaw}}{}{}{
    Built internal web apps with JavaScript and Angular, and a standalone desktop app in Ruby. Co-led Responsive Web Design (RWD) workshops at the InfoMEET conference.
}

\cventry{Aug. 2014 -- Apr. 2016}{Junior Programmer / Web Developer}{\textsc{\newline Lionbridge Technologies, Inc., Warsaw}}{}{}{
}

\cventry{Aug. 2014 -- May 2016}{Web Developer}{\textsc{\newline Cisco Systems, Inc., Warsaw}}{}{}{
    Built and maintained websites for Cisco Systems targeting EMEA markets.
}

\section{Education}

\cventry{2017-2018}{Mobile Web Specialist}{}{}{\textit{Google Developer Challenge Scholarship.}}{} 

\cventry{2016--present}{Computer Science}{BA, part-time}{}{\textit{Polish-Japanese Academy of Information Technology}}{} 

\cventry{2013--2015}{Computer Science}{BA}{}{\textit{Faculty of Mathematics, Informatics and Mechanics}}{University of Warsaw}  % Arguments not required can be left empty

\cventry{2009--2012}{Mathematics}{BA}{}{\textit{Faculty of Mathematics, Informatics and Mechanics}}{University of Warsaw}  % Arguments not required can be left empty

\section{Technical Skills}
JavaScript, TypeScript (Node.js, React, React Native, Next.js, NestJS, Express, D3.js, WebSockets); SQL (PostgreSQL, Redis); Git, Bash; Docker, Kubernetes, GitHub Actions; Azure, AWS (Bedrock, S3), Railway; Grafana, Loki, Prometheus; RabbitMQ, Elasticsearch; AI integration (LLM, text/image analysis), Data scraping; Jest

	
\section{Languages}
	\cvitemwithcomment{English}{Advanced (C1)}{}
        \cvitemwithcomment{Polish}{Native}{}

\bigskip
\bigskip

\small{I hereby consent to the processing of my personal data included in my application for the purposes of the recruitment process, in accordance with the General Data Protection Regulation (EU) 2016/679 (GDPR).}

\end{document}